State of the Practice for Lattice Boltzmann Method Software

### 2021-12-11 StateOfPractice/Papers/LatticeBoltz_SOP-arXiv/LatticeBoltz_SOP.tex
Fixed interview subsection heading
Updates to sections on AHP and Interaction with the Domain Expert

\section{Survey Developers} \label{SecSurvey}

@@

The Analytical Hierarchy Process (AHP) is a decision-making technique that is
used to compare multiple options by multiple criteria. In our work AHP was used
for comparing and ranking the LBM software packages using the overall impression
quality scores that were gathered in the measurement template found in Appendix
~\ref{measurementtemplate2} using the grading template found in Appendix
~\ref{gradingtemplate2}. AHP performs a pairwise analysis using a matrix and
generates an overall score as well as individual quality scores for each
software package. Smith et al. (2016) shows how the AHP is applied to ranking
software based on quality measures \cite{SmithEtAl2016}.

This project used a tool for conducting this process. The tool includes a
sensitivity analysis that was used to ensure that the software package rankings
are appropriate with respect to the uncertainty of the quality scores. The
\href{https://github.com/smiths/AIMSS/blob/master/StateOfPractice/AHP2020/LBM/README.txt}{README}
file of the tool includes requirements and usage information.

@@

The Domain Expert is an important member of the state of the practice assessment
team. Pitfalls exist if non-experts attempt to acquire an authoritative list of
software, or try to definitively rank the software. Non-experts have the problem
that they can only rely on information available on-line, which has the
following drawbacks:
\begin{inparaenum}[i)]
  \item the on-line resources could have false or inaccurate information; and,
  \item the on-line resources could leave out relevant information that is so
in-grained with experts that nobody thinks to explicitly record it.
\end{inparaenum}

Domain experts may be recruited from academia or industry.  The only
requirements are knowledge of the domain and a willingness to be engaged in the
assessment process.  The Domain Expert does not have to be a software developer,
but they should be a user of domain software.  Given that the domain experts are
likely to be busy people, the measurement process cannot put to much of a burden
on their time.  For the current assessment, our Domain Expert (and paper
co-author) is Dr.\ Michael Noseworthy, Professor of Electrical and Computer
Engineering at McMaster University, Co-Director of the McMaster School of
Biomedical Engineering, and Director of Medical Imaging Physics and Engineering
at St. Joseph’s Healthcare, Hamilton, Ontario, Canada.

In advance of the first meeting with the Domain Expert, the expert is asked to
create a list of top software packages in the domain.  This is done to help
the expert get in the right mind set in advance of the meeting.  Moreover,
by doing the exercise in advance, we avoid the potential pitfall of the expert
approving the discovered list of software without giving it adequate thought.

The Domain Experts are asked to vet the collected data and analysis.  In
particular, they are asked to vet the proposed list of software packages and the
AHP ranking.  These interactions can be done either electronically or with
in-person (or virtual) meetings.

>>>>

\subsection{Interview Developers} \label{SecSurvey}

@@

The Analytical Hierarchy Process (AHP) is a decision-making technique that is
used to compare multiple options by multiple criteria. In our work AHP was used
for comparing and ranking the LBM software packages using the overall impression
quality scores that were gathered in the measurement template.  AHP performs a
pairwise analysis using a matrix and generates an overall score as well as
individual quality scores for each software package. \citep{SmithEtAl2016} shows
how AHP is applied to ranking software based on quality measures.

This project used a tool for conducting this process. The tool includes a
sensitivity analysis that was used to ensure that the software package rankings
are appropriate with respect to the uncertainty of the quality scores. For the
sensitivity analysis we modified the score by 10\% for each package and verified
that the overall ranking was stable.  The
\href{https://github.com/smiths/AIMSS/blob/master/StateOfPractice/AHP2020/LBM/README.txt}{README}
file of the tool includes requirements and usage information.

@@

The Domain Expert is an important member of the state of the practice assessment
team. Pitfalls exist if non-experts attempt to acquire an authoritative list of
software, or try to definitively rank the software. Non-experts have the problem
that they can only rely on information available on-line, which has the
following drawbacks:
\begin{inparaenum}[i)]
  \item the on-line resources could have false or inaccurate information; and,
  \item the on-line resources could leave out relevant information that is so
in-grained with experts that nobody thinks to explicitly record it.
\end{inparaenum}
For the current assessment, our Domain Expert (and paper co-author) is Dr.\
Zahra Motamed, Assistant Professor of Mechanical Engineering at McMaster
University, Hamilton, Ontario, Canada.

The Domain Expert has an important role with verifying the list of LBM packages.
In advance of the first meeting with the Domain Expert, they were asked to
create a list of top software packages in the domain.  This is done to help the
expert get in the right mind set in advance of the meeting.  Moreover, by doing
the exercise in advance, we avoid the potential pitfall of the expert approving
the discovered list of software without giving it adequate thought.  The Domain
Expert was also asked to vet the collected data and analysis.  In particular,
they were asked to vet the proposed list of software packages and the AHP
ranking.  These interactions were done via virtual meetings.
